Genome-Wide Association Study

### 2018-01-24 GWAS-comparison.Rmd
run on laptop

# Get population from external files
pop.files <- list.files(path = "../thesis-celiac/Dubois2010_data/",
                        pattern = "cluster_*",
                        full.names = TRUE)
pop <- snp_getSampleInfos(celiac, pop.files)[[1]]
pop.names <- c("Netherlands", "Italy", "UK1", "UK2", "Finland")
# Plot PC1 & PC2
plot(obj.svd, type = "scores", coeff = 2) +
  aes(color = pop.names[pop]) +
  labs(color = "Population", title = NULL) +
  theme(legend.position = c(0.2, 0.75)) + 
  guides(colour = guide_legend(override.aes = list(size = 4)))

>>>>

# Get population from external files
pop.files <- list.files(path = "data", pattern = "cluster_*", full.names = TRUE)
pop <- snp_getSampleInfos(celiac, pop.files)[[1]]
pop.names <- c("Netherlands", "Italy", "UK1", "UK2", "Finland")
# Plot PC1 & PC2
plot(obj.svd, type = "scores", coeff = 2) +
  aes(color = pop.names[pop]) +
  labs(color = "Population", title = NULL) +
  theme(legend.position = c(0.2, 0.75)) + 
  guides(colour = guide_legend(override.aes = list(size = 4)))
